---
title: 'Group/Homework #6'
author: '[Type in Your Name]'
date: "4/28/2022"
output: html_document
---

## Preface/Preamble

You should always have an initial r code chunk that sets up your work environment by loading all the packages you would need for the rest of the document. Fill in the code chunk below.

```{r}
library(tidyverse)
library(gapminder)
library(socviz)
library(ggplot2)
library(dplyr)
library(ggrepel)
library(coefplot)
```

## Chapters 6 and 7 "Where to Go Next" Plus Some Others

**Put `r` code into code chunks and write narrative answers as plain text.**

1. Chapter 6, page 169. "Default plots for models" Run the following model:

```{r}
lm(formula = lifeExp ~ log(gdpPercap) + pop + continent, data = gapminder)
out <- lm(formula = lifeExp ~ log(gdpPercap) + pop + continent, data = gapminder)
plot(out, ask = FALSE)
```

Using the plot() function built into base R to create *all* the plots of the regression results the function generates.

Discuss the ways in which this approach of using the `plot()` function is a) better and b) worse than using the functions in the `broom` library to extract and plot results.

2. Install and load the `coefplot` package, and generate a plot of the regression results from Question 1 above. Be sure to make the plot with the following characteristics: a) red lines/dots b) variables ordered by magnitude, with the large effect on the bottom c) intercept renamed to "Constant".
```{r}

a<- coefplot(out, sort = "magnitude", color="darkred")   
a + scale_y_discrete(name ="Coefficent", labels=c("pop","constant","continentAsia","log(gdpPercap)","continentAmerica","continentOcenia","continetEurope"))

a
```

3. Chapter 7, page 194. Sidebar. Try revisiting your code for the ur-choropleths, but use continuous rather than binned measures, as well as the `viridis` palette. Instead of `pct_black` use the `black` variable. For the population density, divide `pop` by `land_area`. You will need to adjust the `scale_` functions. How do the maps compare to the binned versions? What happens to the population density map, and why?
```{r}
library(viridis)
county_full <- left_join(county_map, county_data, by = "id")
p <- ggplot(data = county_full,
mapping = aes(x = long, y = lat, fill = black,
group = group))
p1 <- p + geom_polygon(color = "gray90", size = 0.05) + coord_equal()
p2 <-  p1 + scale_color_viridis(palette="Greens")+labs(fill = "population density")
p2
```
4. The `maps` library has other map data built in, in addition to the U.S. states. Using similar steps as in the textbook, accomplish the following. Create a world map dataframe (hint: "world" instead of "state"), join it with the `gapminder` data, and plot a world map that fills in countries according to their life expectancy in in 2007.

```{r}
library(maps)
world <- map_data("world")

names(gapminder)[names(gapminder) == 'country'] <- 'region'

head(gapminder)
```

```{r}
world_gap <-left_join(world, gapminder)
head(world_gap)
```
```{r}
p0 <- ggplot(data = subset(world_gap, year = 2007),
             mapping = aes(x = long, y = lat,
                 group = group,
                 fill = lifeExp))

p1 <- p0 + geom_polygon(color = "gray90", size = 0.05) +
    coord_map(projection = "albers", lat0 = 39, lat1 = 45) 

p2 <- p1 + scale_fill_viridis_c(option = "plasma")

p2


```


5. Chapter 7 "Where to go next". As Healy discusses, `sf` implements a standard way to encode and work with real world things ("simple features"). Install and load the package, and skim through the `ggplot2` [reference page on `sf`](https://ggplot2.tidyverse.org/reference/ggsf.html). Create the dataframe `nc` as indicated in the example code.  How are the latitudes and longitudes stored in this data? How is the format different from what you worked with in Chapter 7?

install.packages("sf")
library(sf)
```{r}
nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
ggplot(nc) + geom_sf(aes(fill = AREA))
```

6. Using the `nc` dataframe, plot a map of North Carolina that shades in the counties by the length of the perimeter. For the fill scale, the mid-point should be at 2 and have a diverging color scheme for counties with perimeter less than 2 versus counties with perimeter greater than 2.

```{r}

nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
ggplot(nc) + geom_sf(aes(fill = PERIMETER>=2))+labs(fill = "Perimeter Greater Than TWO" )
```

7. Using one of the built-in data sets (either into `R`, `tidyverse` or `socviz`), create a simple `gganimate` plot. Then, change one of the `gganimate` functions you use to alter the way that the plot is animated. (This question therefore asks for *two* animated plots.) For help, this is [the getting started](https://gganimate.com/articles/gganimate.html) guide, and this is [the reference page](https://gganimate.com/reference/index.html).
```{r}
library(gganimate)
library(gapminder)
library(ggplot2)
```

```{r}
library(gganimate)
anim <- p + 
  transition_states(continent,
                    transition_length = 2,
                    state_length = 1)
anim
```